VariantSpark: Population Scale Clustering of Genotype Information

### 2015-09-04 doc/publications/journal2014/paper.tex
section for neil

\subsection*{R Implementation}
For our R implementation, we read in the VCF file as a table and convert it to a matrix, dropping the columns that don't represent alleles. As with our \variantSpark{} pre-processing, we convert the strings that represent each allele to a numeric value.
We then transpose the matrix, resulting in a data-structure where each row represents an individual.

\subsection*{Python Implementation}
Our Python implementation reads in a VCF file as tab-separated values, and stores it as a pandas dataframe. We convert the allele strings to numeric values and then transpose the dataframe.

%% TODO (and better heading) %%
\subsection*{Personal Genome Project VCF making}
The PGP data.....

>>>>

\subsection*{R Implementation}
For our R implementation, we read in a VCF file as a table and convert it to a matrix, dropping the columns that don't represent alleles. As with our \variantSpark{} pre-processing, we convert the strings that represent each allele to a numeric value.
We then transpose the matrix, resulting in a data-structure where each row represents an individual.

\subsection*{Python Implementation}
Our Python implementation reads in lines from a VCF file as tab-separated values and stores the lines in a pandas DataFrame. The column headings are the individual IDs and the row headings are the allele locations.
We drop the first columns that aren't alleles, and then convert the remaining allele strings to numeric values. We can then transpose the DataFrame. Although to cluster this DataFrame (using sci-kit learn), we simply need to convert it to a matrix with {\sc .as\textunderscore{}matrix()}

%% TODO - NEIL - (and better heading) %%
\subsection*{Personal Genome Project VCF making}
The PGP data.....
